### 2020-01-16 related.tex
Added more related work.

Other work in characterizing supercomputer faults, errors and failures focused on the various systems deployed around the world, primarily at US Department of Energy laboratories.
%
Di et al.~\cite{8809553} developed an in-depth understanding of the failure characteristics of the IBM Blue Gene/Q Mira system at Argonne National Laboratory.

>>>>

Other work in characterizing supercomputer faults, errors and failures focused on the various systems deployed around the world, primarily at US Department of Energy laboratories.
%
Di et al.~\cite{8809553} developed an in-depth understanding of the failure characteristics of the IBM Blue Gene/Q Mira system at Argonne National Laboratory. This work showed that 99.4\% of job failures were due to user behavior, such as errors in the code or misconfiguration. Martino et al.~\cite{6903615} characterized the errors and failures of the Blue Waters Cray XE6/XK7 system at the National Center for Supercomputing Applications (NCSA), at the University of Illinois at Urbana-Champaign. Blue Waters's XK7 partition had the same architecture as Titan. The results showed that 74.4\% of system-wide outages was caused by software.

\fix{More references regarding GPU reliability}
